%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo[circle,noedge,left]{./examples/profile}
\name{Shengfeng }{Li}
% \position{Software Architect{\enskip\cdotp\enskip}Security Expert}
\address{4065 Burbank Drive, Apt.\#1, Baton Rouge, Louisiana, United States}

\mobile{(225) 475-4689}
\email{cs.shengfeng.li@gmail.com}
\homepage{sites.google.com/view/shengfengli/home}
\github{github.com/lishengfeng}
\linkedin{www.linkedin.com/in/shengfeng-li/}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \extrainfo{extra informations}

% \quote{``Be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Company Recruitment Team}
  {Google Inc.\\Software Engineering\\Mountain View, CA, United States}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Software Engineer, University Graduate}
% How the letter is opened
\letteropening{\\Greetings!}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
% \letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Shengfeng Li~~~·~~~Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{About Me}
I have been a professional software developer for the last six years. For the first three years, I worked as a developer at Beijing Brain Cell Software, a company in China that is a subsidiary of Fujitsu of Japan. Then I worked as an Android developer at the Fujitsu office in the following two years. After that, I came to the United States and am pursuing a master's degree in Computer Science. 

My work consists of developing code using Java and Python. I was a technical lead over five programmers on Android-based projects. While working on this project, I taught myself Gradle and Git, showed my team how to use these tools, and designed our branching strategy so that our builds and version control work very smoothly. I am always experimenting with code and new programming languages. As part of my job, I strive to use better algorithms to solve my problem. Through my additional education and work experience, I gained a solid understanding of good coding practices, data structures, and algorithms, as well as practical experience with a variety of programming languages and operating system. I believe my broad technical education and professional software engineering experience would be a valuable asset of your program.

My graduate assistantship is about building a back-end web to help teachers grade and analyze students' submissions. Over 500 students are using my system to submit their homework. Also, I'm very interested in machine learning, especially in the field of deep learning reinforcement learning. I've also chosen multi-agent reinforcement learning as my master project.  I very much hope I can be a useful addition to the team.


\lettersection{Why Google?}
I never thought I could be so close to Google. Google is always my dream company ever since I started learning to program. Google has everything that an employee would expect. I love the Android that Google makes. It helped me find my first software engineer job. I admire the culture of Google. It offers  the most innovative work environment. And working at Google provides employees with the sense of contributing to the worldwide population.

\lettersection{Why Me?}
I have six years of programming experience and proven expertise in agile development processes. I have some successful projects and some of them are still running and making a profit.

I have developed my communication skills from working. Also I can speak Chinese, Japanese, and English. I have the experience to start contributing from day one and I am truly excited about the prospect of getting a start.


\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
